---
title: "Final Project"
author: \textcolor{red}{Aman Singh}
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
fontsize: 12pt
geometry: margin = 1in
header-includes:
  - \usepackage{setspace}\doublespacing
---
$$\textbf{\underline{Introduction:}}$$
\begin{figure}[h]
  \centering\includegraphics[angle = 0,scale = .4]{george}
  \centering\includegraphics[angle = 0,scale = .4]{lebron}
  \caption{George Mikan pictured on the left and Lebron James pictured on the right}
\end{figure}
Sports is a huge part of America, starting from the 1800’s when Baseball was invented in 1834, and then later other sports such as American Football and then Basketball \textcolor{blue}{\cite{baseball}}. Basketball in particular however, really became big in the 1950’s when legends such as George Mikan and Bob Shayes put the NBA on notice. Fast forward to the present, and the NBA players right now such as Lebron James and Stephen Curry have been making the league exciting and fun to watch generating massive amounts of revenue and viewership for the NBA \textcolor{blue}{\cite{viewership}}.
The biggest difference that I see in the picture above is not only the color and the race, but also the fact that it seems that Lebron James has significantly more muscle mass than George Mikans. George Mikans just looks like a skinny tall NBA player that would really suffer in the NBA today. I was curious to see why Geroge Mikans decided to play back in the NBA in the 1950’s because the players back then did not get paid the millions that they are paid currently even after adjusting for inflation. George Mikan's salary in the NBA in the 1950’s was just \$12,000 and after adjusting in the present days’ inflation using the CPI index, only \$169,433.41  \textcolor{blue}{\cite{cpi}}. That is still low for being one of the best players in the NBA today with Lebron James commanding an outstanding salary of \$37,436,858 \textcolor{blue}{\cite{lebron}}. This made me start thinking whether the NBA players now play for the love of the game or if they are chasing a paycheck. I decided to compare 2 NBA players one from the past and one from the future, George Mikan and Lebron James. In 1950-1951 season, George Mikan averaged 28.4 points a game while Lebron James, in the 2017-2018 season where he played all 82 games, averaged 27.5 points per game \textcolor{blue}{\cite{mikan,lebronppg}}. This is surprising and shows that maybe there are other factors that make an NBA player great such as how many shots they have taken, how many shots actually make, and as such there are many other factors then what the points suggest. There are also a lot of historical changes as well such as you can hold the ball as long as you wanted to in the 1950’s because the NBA didn't have the 24 second shot clock violation they do have today which can limit how many points you can shoot \textcolor{blue}{\cite{shotclock}}. I realized that another factor that could seemingly affect the 2 players could be BMI. However, BMI is largely inflated and does not take into account muscle mass. How BMI is calculated in fact takes into only weight and height with the formula given below:
$$BMI = Weight/Height^2$$
where BMI stands for \textcolor{blue}{Body Mass Index}, weight is in \textcolor{blue}{Kilograms} and the height is in \textcolor{blue}{Meters}. I obtained the dataset that I will be observing from Kaggle which listed all the players in the NBA season of 2014-2015 \textcolor{blue}{\cite{dataset}}.

\begin{table}[hbt!]
\centering
\begin{tabular}{ |c|c|c|c|c| } 
 \hline
 Name & Points Per Game & Height & Weight & BMI \\ 
 \hline
 \hline
 George Mikan & 28.4 & 2.08 & 111.13 & 25.613 \\ 
 \hline
 Lebron James & 27.5 & 2.06 & 113.398 & 27.4 \\ 
 \hline
\end{tabular}
\caption{Past NBA stars vs the Present:}
\end{table}

Looking at this table that I made, is really just shows that BMI does not really mean much in the NBA because in terms of BMI, both of these players, who were the best in there respective decades, are considered "overweight". It made me wonder if there are other attributes like I mentioned above if there are other factors involved such as experience, salary, and perhaps even college. This made me come to the colusion that I will use this dataset to analyze: 
$$\textcolor{red}{\textbf{Is performance in the NBA related to more than the physical attributes of an athlete?}}$$
I have noticed that in general a plethora of people have wondered how BMI can affect a players performance on the court. In 2005, there was a study done involving Shaq, one of the heaviest players during that time and it showed that despite being one of the heaviest players in the NBA, his body fat percentage was only 13% which is pretty fit for an athlete overall \textcolor{blue}{\cite{Shaq}}. However, the reason why I decided to not state BMI in my question is because I wanted to include the fact that maybe there are other factors that could be related to performance in the NBA. It has long been stated and there have been players who put in 100% everyday and would get a huge paycheck. However, once they got that paycheck, they wouldn't play as hard anymore and thus could potentially hurt a teams' chance of making the playoffs because they can't sign more NBA players \textcolor{blue}{\cite{money}}. I will be addressing salary and whether it can hurt a team's chances of making the playoffs. In fact, I believe this question is extremely important in understanding if there are many factors in how a player performs on the court, whether the motivation is money or if they are “fit” in terms of BMI, or if it concerns their experience in the NBA. There are many factors which is why I chose this question to truly find out if the performance in the NBA is related to the physical attributes or more than just physical. I believe this question is very important to people who have a passion of the NBA and not only that but also the General Managers in the NBA who might find this analysis useful to see what specific attributes they should look for when they go and get a player, whether its considering salary, experience, or even BMI.
$$\textbf{\underline{Understanding the Dataset:}}$$
In this section, I will make an attempt to understand the dataset and understand the representation of each column. When I downloaded this dataset, I noticed that there were \textcolor{blue}{490} rows, with \textcolor{blue}{34} columns depicting a single player's stats as well as other personal information. However, there were a lot of NA's in the dataset. I believe that the website that this data was scraped from had a lot of missing values for a lot of players and thus leading to a lot of NA’s. In order to use CV-Lasso, and Bootstrap, we are supposed to not have any NA’s in the dataset which I also address later. I also noticed that the author of this dataset wrote \textcolor{red}{collage} instead of \textcolor{blue}{college}, so I decided to change the name to help with later analysis. I believe this dataset is very useful becauase with it not only shows how points they have shot, but also how much shots they have attempted as well which can show a percentage of there efficiency.I also made a table below showing the interpretation of each abbreviated column because a lot of people that don't understand the NBA will not understand the columns that are in this dataset. I also have to understand the fact that there is a huge limitation in the dataset. It only shows relevant statistics in the 2014-2015 year and thus if I wanted to know if BMI and Salary really have a correlation, I would not be able to really analyze that. To be further specific, if I wanted to analyze a player who in the 2014-2015 season had a BMI less than 25 and earned only 1 million per year in salary and than thus compare it to when he gets a huge salary bonus in the offseason, ie 5 million, to see if that affects his game or not, I would not be able to analyze that. It could be that he gets more lazy during the off-season reaping the rewards of his hard work and thus see a shortage both in his performance on the field and his physical body as well. I would not be able to know if the salary or BMI truly affects NBA players performance on the court. However, I can try my best to use the data that I have and try to answer the question.

```{R Loading Dataset,echo = FALSE}
nba_players_stats<- read.csv("~/Desktop/Economics/Empirical Project file/players_stats.csv")
```
\begin{table}[ht]
    \caption{Interpretation of the columns in the dataset:}
    \begin{minipage}{.5\linewidth}
      \caption{Part A:}
      \centering
        \begin{tabular}{|l|l|}
            \hline
            \textcolor{blue}{Name of columns} & \textcolor{red}{Interpretation} \\ 
            \hline
            \hline
            Name & Name  \\ 
            \hline
            Games.Played & Total Games Played  \\ 
            \hline
            MIN & Minutes Played \\
            \hline
            PTS & Points Made \\
            \hline
            FGM & Field Goals Made \\
            \hline
            FGA & Field Goals Att. \\
            \hline
            FG. & Field Goal Perc. \\
            \hline
            X3PM & 3 Points Made \\
            \hline
            X3PA & 3 points Att. \\
            \hline
            X3P. & 3 Point Perc. \\
            \hline
            FTM & Free Throws Made \\
            \hline
            FTA & Free Throws Att. \\
            \hline
            FT. & Free Throw Perc.\\
            \hline
            OREB & Offensive Rebounds \\
            \hline
            DREB & Defensive Rebounds\\
            \hline
            REB & Rebounds Made \\
            \hline
            AST & Assists Made \\
            \hline
        \end{tabular}
    \end{minipage}%
    \begin{minipage}{.5\linewidth}
      \centering
        \caption{Part B:}
        \begin{tabular}{|l|l|}
            \hline
            \textcolor{blue}{Name of columns} & \textcolor{red}{Interpretation} \\
            \hline
            \hline
            STL & Total Steals \\
            \hline 
            BLK & Total Blocks \\
            \hline
            TOV & Total Turnovers\\
            \hline
            PF & Total Personal Fouls \\
            \hline
            EFF & Efficiency on the court \\
            \hline
            AST.TOV & Assists/Turnover Perc.\\
            \hline
            STL.TOV & Steals/Turnover Perc. \\
            \hline
            Age & Age \\
            \hline
            BirthPlace & Birth Place \\
            \hline
            Birthdate & Birth Date \\
            \hline
            Collage & College \\
            \hline
            Experience & Experience in the NBA\\
            \hline
            Height & Height \\
            \hline
            Pos & Position on Team \\
            \hline
            Team & Team \\
            \hline
            Weight & Weight \\
            \hline
            BMI & Body Mass Index \\
            \hline
        \end{tabular}
    \end{minipage} 
\end{table}
```{r Changing column Name,echo=FALSE}
colnames(nba_players_stats)[28] = "College"
```


$$\textbf{\underline{Cleaning the Data:}}$$
When I first imported the dataset, I decided to replace the  NA’s with meaningful insights. I scoured the web and eventually settled on a website to extract all my insights from \textcolor{blue}{\cite{fillna}}. The first NA’s that I found were in the \textcolor{blue}{Age} column and so I used the website to find their respective age during the 2014-2015 season. The next column that I filled in the NA’s for was the \textcolor{blue}{weight} category, which I also filled in using pounds but I realized BMI uses kilograms, which is why I decided to divide by \textcolor{red}{2.205} to convert into Kilograms. The column I filled in after that was their respective \textcolor{blue}{heights} which I filled in remembering BMI, in centimeters for easier calculation. I also then calculated the \textcolor{blue}{BMI’s} for the NBA players that did not have their height & weight originally filled in. I then also filled in the \textcolor{blue}{position} that each player respectively played in the NBA as well. I believe that can lead to some very personal and interesting insights of the data regarding position and points, or position and comparing it to weight respectively even. Upon looking at the \textcolor{blue}{Experience} column, I realized that the class of the column was a factor which you cannot thus use to graph meaningful insights. Also, a problem in that column was that the rookies in the year of 2014-2015 were listed as \textcolor{red}{“R”}. I thus changed the class of the column, replaced the “R” with 0 to indicate they have no experience in the NBA, and filled in the NA values as well. I then decided to add 2 more columns, being \textcolor{blue}{Salary} and \textcolor{blue}{Playoffs.made}. I decided to make the column Salary because I wanted to see if salary could be a big factor in the NBA in terms of their BMI, or their performance on the court. The salaries that I indexed in are adjusted according to the year 2020’s inflation rate \textcolor{blue}{\cite{nba_salary}}. I also decided to make a column called playoffs.made as well to see if depending on multiple factors, if the player was able to play in the playoffs, and I personally believe that it can lead to some meaningful insights. The Playoffs.made column is simply a column indicating that if your team made the playoffs, it would say Yes, and if not, No. The teams that made it to the playoffs in the 2014-2015 season were the \textbf{Atlanta Hawks}\includegraphics[angle = 0,scale = .03]{hawks}, the \textbf{Milwaukee Bucks}\includegraphics[angle = 0,scale = .2]{bucks}, the \textbf{Golden State Warriors}\includegraphics[angle = 0,scale = .079]{warriors}, the \textbf{Cleveland Cavaliers}\includegraphics[angle = 0,scale = .059]{cavaliers}, the \textbf{Boston Celtics}\includegraphics[angle = 0,scale = .079]{celtics}, the \textbf{Los Angeles Clippers}\includegraphics[angle = 0,scale = .039]{clippers}, the \textbf{Toronto Raptors}\includegraphics[angle = 0,scale = .063]{raptors}, and the \textbf{Brooklyn Nets}\includegraphics[angle = 0,scale = .059]{nets}.The Golden State Warriors won that year, playing against the Cleveland Cavaliers in the Finals.
\begin{figure}[h]
  \centering\includegraphics[angle = 0,scale = .5]{champions}
  \caption{Warriors win first championship after 40 years}
\end{figure}
```{r Adding missing data,echo=FALSE}
nba_players_stats$Team = as.character(nba_players_stats$Team)
nba_players_stats$Birth_Place = as.character(nba_players_stats$Birth_Place)
nba_players_stats$Birthdate = as.character.Date(nba_players_stats$Birthdate)
nba_players_stats$College = as.character(nba_players_stats$College)
#Amar'e Stoudemire
nba_players_stats$Height[16] = 208.28
nba_players_stats$Weight[16] = 245/2.205
nba_players_stats$BMI[16] = (nba_players_stats$Weight[16]/(nba_players_stats$Height[16])^2)*10000
nba_players_stats$Age[16] = 32
nba_players_stats$Team[16] = "NYK"
nba_players_stats$College[16] = "University of Miami"
nba_players_stats$Birth_Place[16] = "us"
nba_players_stats$Birthdate[16] = "16-Nov-82"
#Anderson Varejao
nba_players_stats$Height[18] = 210.82
nba_players_stats$Weight[18] = 273/2.205
nba_players_stats$BMI[18] = (nba_players_stats$Weight[18]/(nba_players_stats$Height[18])^2)*10000
nba_players_stats$Age[18] = 32
nba_players_stats$Team[18] = "CLE"
nba_players_stats$College[18] = "no college"
nba_players_stats$Birth_Place[18] = "br"
nba_players_stats$Birthdate[18] = "28-Sep-82"
#Andrew Wiggins
nba_players_stats$Height[28] = 203.2
nba_players_stats$Weight[28] = 194/2.205
nba_players_stats$BMI[28] = (nba_players_stats$Weight[28]/(nba_players_stats$Height[28])^2)*10000
nba_players_stats$Age[28] = 19
nba_players_stats$Team[28] = "MIN"
nba_players_stats$College[28] = "University of Kansas"
nba_players_stats$Birth_Place[28] = "ca"
nba_players_stats$Birthdate[28] = "23-Feb-95"
#Anthony Tolliver
nba_players_stats$Height[32] = 203.2
nba_players_stats$Weight[32] = 249/2.205
nba_players_stats$BMI[32] = (nba_players_stats$Weight[32]/(nba_players_stats$Height[32])^2)*10000
nba_players_stats$Age[32] = 29
nba_players_stats$Team[32] = "DET"
nba_players_stats$College[32] = "Creighton University"
nba_players_stats$Birth_Place[32] = "us"
nba_players_stats$Birthdate[32] = "1-Jun-85"
#Beno Udrih
nba_players_stats$Height[42] = 203.2
nba_players_stats$Weight[42] = 190.5/2.205
nba_players_stats$BMI[42] = (nba_players_stats$Weight[42]/(nba_players_stats$Height[42])^2)*10000
nba_players_stats$Age[42] = 32
nba_players_stats$Team[42] = "MEM"
nba_players_stats$College[42] = "no college"
nba_players_stats$Birth_Place[42] = "sl"
nba_players_stats$Birthdate[42] = "5-Jul-82"
#Brandan Wright
nba_players_stats$Height[49] = 208.28
nba_players_stats$Weight[49] = 235/2.205
nba_players_stats$BMI[49] = (nba_players_stats$Weight[49]/(nba_players_stats$Height[49])^2)*10000
nba_players_stats$Age[49] = 27
nba_players_stats$Team[49] = "BOS"
nba_players_stats$College[49] = "University of North Carolina at Chapel Hill"
nba_players_stats$Birth_Place[49] = "us"
nba_players_stats$Birthdate[49] = "5-Oct-87"
#Charlie Villanueva
nba_players_stats$Height[69] = 210.82
nba_players_stats$Weight[69] = 240/2.205
nba_players_stats$BMI[69] = (nba_players_stats$Weight[69]/(nba_players_stats$Height[69])^2)*10000
nba_players_stats$Age[69] = 30
nba_players_stats$Team[69] = "DAL"
nba_players_stats$College[69] = "University of Connecticut"
nba_players_stats$Birth_Place[69] = "us"
nba_players_stats$Birthdate[69] = "24-Aug-84"
#CJ Wilcox
nba_players_stats$Height[81] = 195.58
nba_players_stats$Weight[81] = 194/2.205
nba_players_stats$BMI[81] = (nba_players_stats$Weight[81]/(nba_players_stats$Height[81])^2)*10000
nba_players_stats$Age[81] = 24
nba_players_stats$Team[81] = "LAC"
nba_players_stats$College[81] = "University of Washington"
nba_players_stats$Birth_Place[81] = "us"
nba_players_stats$Birthdate[81] = "30-Dec-90"
#Cody Zeller
nba_players_stats$Height[84] = 195.58
nba_players_stats$Weight[84] = 194/2.205
nba_players_stats$BMI[84] = (nba_players_stats$Weight[84]/(nba_players_stats$Height[84])^2)*10000
nba_players_stats$Age[84] = 24
nba_players_stats$Team[84] = "CHA"
nba_players_stats$College[84] = "Indiana University Bloomington"
nba_players_stats$Birth_Place[84] = "us"
nba_players_stats$Birthdate[84] = "5-Oct-92"
#David Wear
nba_players_stats$Height[105] = 208.28
nba_players_stats$Weight[105] = 225/2.205
nba_players_stats$BMI[105] = (nba_players_stats$Weight[105]/(nba_players_stats$Height[105])^2)*10000
nba_players_stats$Age[105] = 24
nba_players_stats$Team[105] = "SAC"
nba_players_stats$College[105] = "University of California, Los Angeles"
nba_players_stats$Birth_Place[105] = "us"
nba_players_stats$Birthdate[105] = "21-Sep-90"
#Deron Williams
nba_players_stats$Height[113] = 190.5
nba_players_stats$Weight[113] = 201/2.205
nba_players_stats$BMI[113] = (nba_players_stats$Weight[113]/(nba_players_stats$Height[113])^2)*10000
nba_players_stats$Age[113] = 30
nba_players_stats$Team[113] = "BKN"
nba_players_stats$College[113] = "University of Illinois at Urbana-Champaign"
nba_players_stats$Birth_Place[113] = "us"
nba_players_stats$Birthdate[113] = "26-Jun-84"
#Derrick Williams
nba_players_stats$Height[116] = 203.2
nba_players_stats$Weight[116] = 240/2.205
nba_players_stats$BMI[116] = (nba_players_stats$Weight[116]/(nba_players_stats$Height[116])^2)*10000
nba_players_stats$Age[116] = 23
nba_players_stats$Team[116] = "SAC"
nba_players_stats$College[116] = "University of Arizona"
nba_players_stats$Birth_Place[116] = "us"
nba_players_stats$Birthdate[116] = "25-May-91"
#Dion Waiters
nba_players_stats$Height[120] = 193
nba_players_stats$Weight[120] = 216/2.205
nba_players_stats$BMI[120] = (nba_players_stats$Weight[120]/(nba_players_stats$Height[120])^2)*10000
nba_players_stats$Age[120] = 23
nba_players_stats$Team[120] = "CLE"
nba_players_stats$College[120] = "Syracuse University"
nba_players_stats$Birth_Place[120] = "us"
nba_players_stats$Birthdate[120] = "10-Dec-91"
#Dorell Wright
nba_players_stats$Height[124] = 205.74
nba_players_stats$Weight[124] = 215/2.205
nba_players_stats$BMI[124] = (nba_players_stats$Weight[124]/(nba_players_stats$Height[124])^2)*10000
nba_players_stats$Age[124] = 29
nba_players_stats$Team[124] = "POR"
nba_players_stats$College[124] = "no college"
nba_players_stats$Birth_Place[124] = "us"
nba_players_stats$Birthdate[124] = "2-Dec-85"
#Dwyane Wade
nba_players_stats$Height[132] = 193.04
nba_players_stats$Weight[132] = 220/2.205
nba_players_stats$BMI[132] = (nba_players_stats$Weight[132]/(nba_players_stats$Height[132])^2)*10000
nba_players_stats$Age[132] = 33
nba_players_stats$Team[132] = "MIA"
nba_players_stats$College[132] = "Marquette University"
nba_players_stats$Birth_Place[132] = "us"
nba_players_stats$Birthdate[132] = "17-Jan-82"
#Ekpe Udoh
nba_players_stats$Height[136] = 208.28
nba_players_stats$Weight[136] = 245/2.205
nba_players_stats$BMI[136] = (nba_players_stats$Weight[136]/(nba_players_stats$Height[136])^2)*10000
nba_players_stats$Age[136] = 27
nba_players_stats$Team[136] = "LAC"
nba_players_stats$College[136] = "University of Michigan"
nba_players_stats$Birth_Place[136] = "us"
nba_players_stats$Birthdate[136] = "20-May-87"
#Elijah Millsap
nba_players_stats$Height[138] = 198.12
nba_players_stats$Weight[138] = 216/2.205
nba_players_stats$BMI[138] = (nba_players_stats$Weight[138]/(nba_players_stats$Height[138])^2)*10000
nba_players_stats$Age[138] = 27
nba_players_stats$Team[138] = "MIL"
nba_players_stats$College[138] = "University of Alabama at Birmigham"
nba_players_stats$Birth_Place[138] = "us"
nba_players_stats$Birthdate[138] = "12-Aug-87"
#Elliot Williams
nba_players_stats$Height[139] = 195.58
nba_players_stats$Weight[139] = 190/2.205
nba_players_stats$BMI[139] = (nba_players_stats$Weight[139]/(nba_players_stats$Height[139])^2)*10000
nba_players_stats$Age[139] = 25
nba_players_stats$Team[139] = "UTA"
nba_players_stats$College[139] = "University of Memphis"
nba_players_stats$Birth_Place[139] = "us"
nba_players_stats$Birthdate[139] = "20-Jun-89"
#Festus Ezeli
nba_players_stats$Height[149] = 205.74
nba_players_stats$Weight[149] = 265/2.205
nba_players_stats$BMI[149] = (nba_players_stats$Weight[149]/(nba_players_stats$Height[149])^2)*10000
nba_players_stats$Age[149] = 25
nba_players_stats$Team[149] = "GSW"
nba_players_stats$College[149] = "Vanderbilt University"
nba_players_stats$Birth_Place[149] = "ng"
nba_players_stats$Birthdate[149] = "21-Oct-89"
#Gerald Wallace
nba_players_stats$Height[159] = 200.66
nba_players_stats$Weight[159] = 220/2.205
nba_players_stats$BMI[159] = (nba_players_stats$Weight[159]/(nba_players_stats$Height[159])^2)*10000
nba_players_stats$Age[159] = 32
nba_players_stats$Team[159] = "BOS"
nba_players_stats$College[159] = "Alabama Crimson Tide"
nba_players_stats$Birth_Place[159] = "us"
nba_players_stats$Birthdate[159] = "23-Jul-82"
#Gigi Datome
nba_players_stats$Height[161] = 203.2
nba_players_stats$Weight[161] = 216/2.205
nba_players_stats$BMI[161] = (nba_players_stats$Weight[161]/(nba_players_stats$Height[161])^2)*10000
nba_players_stats$Age[161] = 27
nba_players_stats$Team[161] = "DET"
nba_players_stats$College[161] = "no college"
nba_players_stats$Birth_Place[161] = "itl"
nba_players_stats$Birthdate[161] = "27-Nov-87"
#Glenn Robinson III
nba_players_stats$Height[164] = 198.12
nba_players_stats$Weight[164] = 223/2.205
nba_players_stats$BMI[164] = (nba_players_stats$Weight[164]/(nba_players_stats$Height[164])^2)*10000
nba_players_stats$Age[164] = 21
nba_players_stats$Team[164] = "MIN"
nba_players_stats$College[164] = "University of Michigan"
nba_players_stats$Birth_Place[164] = "us"
nba_players_stats$Birthdate[164] = "8-Jan-94"
#Hassan Whiteside
nba_players_stats$Height[174] = 213.36
nba_players_stats$Weight[174] = 265/2.205
nba_players_stats$BMI[174] = (nba_players_stats$Weight[174]/(nba_players_stats$Height[174])^2)*10000
nba_players_stats$Age[174] = 25
nba_players_stats$Team[174] = "MIA"
nba_players_stats$College[174] = "Marshall University"
nba_players_stats$Birth_Place[174] = "us"
nba_players_stats$Birthdate[174] = "13-Jun-89"
#Hedo Turkoglu
nba_players_stats$Height[175] = 208.28
nba_players_stats$Weight[175] = 220/2.205
nba_players_stats$BMI[175] = (nba_players_stats$Weight[175]/(nba_players_stats$Height[175])^2)*10000
nba_players_stats$Age[175] = 35
nba_players_stats$Team[175] = "LAC"
nba_players_stats$College[175] = "no college"
nba_players_stats$Birth_Place[175] = "tu"
nba_players_stats$Birthdate[175] = "19-Mar-79"
#Henry Sims
nba_players_stats$Height[176] = 208.28
nba_players_stats$Weight[176] = 247/2.205
nba_players_stats$BMI[176] = (nba_players_stats$Weight[176]/(nba_players_stats$Height[176])^2)*10000
nba_players_stats$Age[176] = 24
nba_players_stats$Team[176] = "PHI"
nba_players_stats$College[176] = "Georgetown University"
nba_players_stats$Birth_Place[176] = "tu"
nba_players_stats$Birthdate[176] = "27-Mar-90"
#Henry Walker
nba_players_stats$Height[177] = 198.12
nba_players_stats$Weight[177] = 220/2.205
nba_players_stats$BMI[177] = (nba_players_stats$Weight[177]/(nba_players_stats$Height[177])^2)*10000
nba_players_stats$Age[177] = 27
nba_players_stats$Team[177] = "MIA"
nba_players_stats$College[177] = "Kansas State University"
nba_players_stats$Birth_Place[177] = "us"
nba_players_stats$Birthdate[177] = "9-Oct-87"
#Hollis Thompson
nba_players_stats$Height[178] = 203.2
nba_players_stats$Weight[178] = 205/2.205
nba_players_stats$BMI[178] = (nba_players_stats$Weight[178]/(nba_players_stats$Height[178])^2)*10000
nba_players_stats$Age[178] = 23
nba_players_stats$Team[178] = "PHI"
nba_players_stats$College[178] = "Georgetown University"
nba_players_stats$Birth_Place[178] = "us"
nba_players_stats$Birthdate[178] = "3-Apr-91"
#Ish Smith
nba_players_stats$Height[184] = 182.88
nba_players_stats$Weight[184] = 174/2.205
nba_players_stats$BMI[184] = (nba_players_stats$Weight[184]/(nba_players_stats$Height[184])^2)*10000
nba_players_stats$Age[184] = 26
nba_players_stats$Team[184] = "OKC"
nba_players_stats$College[184] = "Wake Forest University"
nba_players_stats$Birth_Place[184] = "us"
nba_players_stats$Birthdate[184] = "5-Jul-88"
#Jabari Parker
nba_players_stats$Height[187] = 203.2
nba_players_stats$Weight[187] = 245/2.205
nba_players_stats$BMI[187] = (nba_players_stats$Weight[187]/(nba_players_stats$Height[187])^2)*10000
nba_players_stats$Age[187] = 19
nba_players_stats$Team[187] = "MIL"
nba_players_stats$College[187] = "Duke University"
nba_players_stats$Birth_Place[187] = "us"
nba_players_stats$Birthdate[187] = "15-Mar-95"
#JaKarr Sampson
nba_players_stats$Height[190] = 200.66
nba_players_stats$Weight[190] = 214/2.205
nba_players_stats$BMI[190] = (nba_players_stats$Weight[190]/(nba_players_stats$Height[190])^2)*10000
nba_players_stats$Age[190] = 21
nba_players_stats$Team[190] = "PHI"
nba_players_stats$College[190] = "St John's University Queens Campus"
nba_players_stats$Birth_Place[190] = "us"
nba_players_stats$Birthdate[190] = "20-Mar-93"
#James Young
nba_players_stats$Height[199] = 198.12
nba_players_stats$Weight[199] = 216/2.205
nba_players_stats$BMI[199] = (nba_players_stats$Weight[199]/(nba_players_stats$Height[199])^2)*10000
nba_players_stats$Age[199] = 19
nba_players_stats$Team[199] = "BOS"
nba_players_stats$College[199] = "University of Kentucky"
nba_players_stats$Birth_Place[199] = "us"
nba_players_stats$Birthdate[199] = "16-Aug-95"
#Jarnell Stokes
nba_players_stats$Height[205] = 205.74
nba_players_stats$Weight[205] = 249/2.205
nba_players_stats$BMI[205] = (nba_players_stats$Weight[205]/(nba_players_stats$Height[205])^2)*10000
nba_players_stats$Age[205] = 21
nba_players_stats$Team[205] = "MEM"
nba_players_stats$College[205] = "University of Tennessee"
nba_players_stats$Birth_Place[205] = "us"
nba_players_stats$Birthdate[205] = "7-Jan-94"
#Jason Smith
nba_players_stats$Height[209] = 213.36
nba_players_stats$Weight[209] = 240/2.205
nba_players_stats$BMI[209] = (nba_players_stats$Weight[209]/(nba_players_stats$Height[209])^2)*10000
nba_players_stats$Age[209] = 28
nba_players_stats$Team[209] = "NYK"
nba_players_stats$College[209] = "Colorado State University"
nba_players_stats$Birth_Place[209] = "us"
nba_players_stats$Birthdate[209] = "2-Mar-86"
#Jason Terry
nba_players_stats$Height[210] = 187.96
nba_players_stats$Weight[210] = 185/2.205
nba_players_stats$BMI[210] = (nba_players_stats$Weight[210]/(nba_players_stats$Height[210])^2)*10000
nba_players_stats$Age[210] = 37
nba_players_stats$Team[210] = "HOU"
nba_players_stats$College[210] = "University of Arizona"
nba_players_stats$Birth_Place[210] = "us"
nba_players_stats$Birthdate[210] = "15-Sep-77"
#Jason Thompson
nba_players_stats$Height[211] = 210.82
nba_players_stats$Weight[211] = 249/2.205
nba_players_stats$BMI[211] = (nba_players_stats$Weight[211]/(nba_players_stats$Height[211])^2)*10000
nba_players_stats$Age[211] = 28
nba_players_stats$Team[211] = "SAC"
nba_players_stats$College[211] = "Rider University"
nba_players_stats$Birth_Place[211] = "us"
nba_players_stats$Birthdate[211] = "21-Jul-86"
#Jeff Withey
nba_players_stats$Height[217] = 213.36
nba_players_stats$Weight[217] = 229/2.205
nba_players_stats$BMI[217] = (nba_players_stats$Weight[217]/(nba_players_stats$Height[217])^2)*10000
nba_players_stats$Age[217] = 24
nba_players_stats$Team[217] = "NOP"
nba_players_stats$College[217] = "University of Kansas"
nba_players_stats$Birth_Place[217] = "us"
nba_players_stats$Birthdate[217] = "7-Mar-90"
#John Salmons
nba_players_stats$Height[243] = 198.12
nba_players_stats$Weight[243] = 207/2.205
nba_players_stats$BMI[243] = (nba_players_stats$Weight[243]/(nba_players_stats$Height[243])^2)*10000
nba_players_stats$Age[243] = 35
nba_players_stats$Team[243] = "NOP"
nba_players_stats$College[243] = "University of Miami"
nba_players_stats$Birth_Place[243] = "us"
nba_players_stats$Birthdate[243] = "12-Dec-79"
#John Wall
nba_players_stats$Height[244] = 193.04
nba_players_stats$Weight[244] = 209/2.205
nba_players_stats$BMI[244] = (nba_players_stats$Weight[244]/(nba_players_stats$Height[244])^2)*10000
nba_players_stats$Age[244] = 24
nba_players_stats$Team[244] = "WAS"
nba_players_stats$College[244] = "University of Kentucky"
nba_players_stats$Birth_Place[244] = "us"
nba_players_stats$Birthdate[244] = "6-Sep-90"
#Josh Smith
nba_players_stats$Height[257] = 205.74
nba_players_stats$Weight[257] = 225/2.205
nba_players_stats$BMI[257] = (nba_players_stats$Weight[257]/(nba_players_stats$Height[257])^2)*10000
nba_players_stats$Age[257] = 29
nba_players_stats$Team[257] = "HOU"
nba_players_stats$College[257] = "no college"
nba_players_stats$Birth_Place[257] = "us"
nba_players_stats$Birthdate[257] = "5-Dec-85"
#Jusuf Nurkic
nba_players_stats$Height[263] = 213.36
nba_players_stats$Weight[263] = 290/2.205
nba_players_stats$BMI[263] = (nba_players_stats$Weight[263]/(nba_players_stats$Height[263])^2)*10000
nba_players_stats$Age[263] = 20
nba_players_stats$Team[263] = "DEN"
nba_players_stats$College[263] = "no college"
nba_players_stats$Birth_Place[263] = "b&h"
nba_players_stats$Birthdate[263] = "23-Aug-94"
#Lance Thomas
nba_players_stats$Height[295] = 203.2
nba_players_stats$Weight[295] = 240/2.205
nba_players_stats$BMI[295] = (nba_players_stats$Weight[295]/(nba_players_stats$Height[295])^2)*10000
nba_players_stats$Age[295] = 26
nba_players_stats$Team[295] = "OKC"
nba_players_stats$College[295] = "Duke University"
nba_players_stats$Birth_Place[295] = "us"
nba_players_stats$Birthdate[295] = "24-Apr-88"
#Larry Sanders
nba_players_stats$Height[299] = 210.82
nba_players_stats$Weight[299] = 229/2.205
nba_players_stats$BMI[299] = (nba_players_stats$Weight[299]/(nba_players_stats$Height[299])^2)*10000
nba_players_stats$Age[299] = 26
nba_players_stats$Team[299] = "MIL"
nba_players_stats$College[299] = "Virginia Commonwealth University"
nba_players_stats$Birth_Place[299] = "us"
nba_players_stats$Birthdate[299] = "21-Nov-88"
#Marcus Thornton
nba_players_stats$Height[320] = 193.04
nba_players_stats$Weight[320] = 205/2.205
nba_players_stats$BMI[320] = (nba_players_stats$Weight[320]/(nba_players_stats$Height[320])^2)*10000
nba_players_stats$Age[320] = 27
nba_players_stats$Team[320] = "BOS"
nba_players_stats$College[320] = "Killgore College"
nba_players_stats$Birth_Place[320] = "us"
nba_players_stats$Birthdate[320] = "5-Jun-87"
#Martell Webster
nba_players_stats$Height[325] = 200.66
nba_players_stats$Weight[325] = 229/2.205
nba_players_stats$BMI[325] = (nba_players_stats$Weight[325]/(nba_players_stats$Height[325])^2)*10000
nba_players_stats$Age[325] = 28
nba_players_stats$Team[325] = "WAS"
nba_players_stats$College[325] = "no college"
nba_players_stats$Birth_Place[325] = "us"
nba_players_stats$Birthdate[325] = "4-Dec-86"
#Miroslav Raduljica
nba_players_stats$Height[342] = 213.36
nba_players_stats$Weight[342] = 243/2.205
nba_players_stats$BMI[342] = (nba_players_stats$Weight[342]/(nba_players_stats$Height[342])^2)*10000
nba_players_stats$Age[342] = 27
nba_players_stats$Team[342] = "LAC"
nba_players_stats$College[342] = "no college"
nba_players_stats$Birth_Place[342] = "sfry"
nba_players_stats$Birthdate[342] = "5-Jan-88"
#Mirza Teletovic
nba_players_stats$Height[343] = 205.74
nba_players_stats$Weight[343] = 243/2.205
nba_players_stats$BMI[343] = (nba_players_stats$Weight[343]/(nba_players_stats$Height[343])^2)*10000
nba_players_stats$Age[343] = 29
nba_players_stats$Team[343] = "BKN"
nba_players_stats$College[343] = "no college"
nba_players_stats$Birth_Place[343] = "sfry"
nba_players_stats$Birthdate[343] = "18-Sep-85"
#Nate Robinson
nba_players_stats$Height[347] = 175.26
nba_players_stats$Weight[347] = 181/2.205
nba_players_stats$BMI[347] = (nba_players_stats$Weight[347]/(nba_players_stats$Height[347])^2)*10000
nba_players_stats$Age[347] = 30
nba_players_stats$Team[347] = "DEN"
nba_players_stats$College[347] = "University of Washington"
nba_players_stats$Birth_Place[347] = "us"
nba_players_stats$Birthdate[347] = "31-May-84"
#Nate Wolters
nba_players_stats$Height[348] = 193.04
nba_players_stats$Weight[348] = 190/2.205
nba_players_stats$BMI[348] = (nba_players_stats$Weight[348]/(nba_players_stats$Height[348])^2)*10000
nba_players_stats$Age[348] = 23
nba_players_stats$Team[348] = "MIL"
nba_players_stats$College[348] = "South Dakota State University"
nba_players_stats$Birth_Place[348] = "us"
nba_players_stats$Birthdate[348] = "15-May-91"
#Nick Young
nba_players_stats$Height[355] = 200.66
nba_players_stats$Weight[355] = 210/2.205
nba_players_stats$BMI[355] = (nba_players_stats$Weight[355]/(nba_players_stats$Height[355])^2)*10000
nba_players_stats$Age[355] = 29
nba_players_stats$Team[355] = "LAL"
nba_players_stats$College[355] = "University of Southern California"
nba_players_stats$Birth_Place[355] = "us"
nba_players_stats$Birthdate[355] = "1-Jun-85"
#Nikola Pekovic
nba_players_stats$Height[359] = 210.82
nba_players_stats$Weight[359] = 307/2.205
nba_players_stats$BMI[359] = (nba_players_stats$Weight[359]/(nba_players_stats$Height[359])^2)*10000
nba_players_stats$Age[359] = 29
nba_players_stats$Team[359] = "MIN"
nba_players_stats$College[359] = "no college"
nba_players_stats$Birth_Place[359] = "sfry"
nba_players_stats$Birthdate[359] = "3-Jan-86"
#Patrick Patterson
nba_players_stats$Height[371] = 205.74
nba_players_stats$Weight[371] = 229/2.205
nba_players_stats$BMI[371] = (nba_players_stats$Weight[371]/(nba_players_stats$Height[371])^2)*10000
nba_players_stats$Age[371] = 25
nba_players_stats$Team[371] = "TOR"
nba_players_stats$College[371] = "University of Kentucky"
nba_players_stats$Birth_Place[371] = "us"
nba_players_stats$Birthdate[371] = "14-Mar-89"
#PJ Tucker
nba_players_stats$Height[381] = 195.58
nba_players_stats$Weight[381] = 245/2.205
nba_players_stats$BMI[381] = (nba_players_stats$Weight[381]/(nba_players_stats$Height[381])^2)*10000
nba_players_stats$Age[381] = 29
nba_players_stats$Team[381] = "PHX"
nba_players_stats$College[381] = "University of Texas"
nba_players_stats$Birth_Place[381] = "us"
nba_players_stats$Birthdate[381] = "5-May-85"
#Reggie Williams
nba_players_stats$Height[394] = 193.04
nba_players_stats$Weight[394] = 212/2.205
nba_players_stats$BMI[394] = (nba_players_stats$Weight[394]/(nba_players_stats$Height[394])^2)*10000
nba_players_stats$Age[394] = 31
nba_players_stats$Team[394] = "MIA"
nba_players_stats$College[394] = "Virginia Military Institute"
nba_players_stats$Birth_Place[394] = "us"
nba_players_stats$Birthdate[394] = "14-Sep-86"
#Ricky Ledo
nba_players_stats$Height[396] = 200.66
nba_players_stats$Weight[396] = 195/2.205
nba_players_stats$BMI[396] = (nba_players_stats$Weight[396]/(nba_players_stats$Height[396])^2)*10000
nba_players_stats$Age[396] = 22
nba_players_stats$Team[396] = "DAL"
nba_players_stats$College[396] = "Providence College"
nba_players_stats$Birth_Place[396] = "us"
nba_players_stats$Birthdate[396] = "10-Sep-92"
#Robert Sacre
nba_players_stats$Height[400] = 213.36
nba_players_stats$Weight[400] = 269/2.205
nba_players_stats$BMI[400] = (nba_players_stats$Weight[400]/(nba_players_stats$Height[400])^2)*10000
nba_players_stats$Age[400] = 25
nba_players_stats$Team[400] = "LAL"
nba_players_stats$College[400] = "Gonzaga University"
nba_players_stats$Birth_Place[400] = "us"
nba_players_stats$Birthdate[400] = "6-Jun-89"
#Ronny Turiaf
nba_players_stats$Height[405] = 208.28
nba_players_stats$Weight[405] = 240/2.205
nba_players_stats$BMI[405] = (nba_players_stats$Weight[405]/(nba_players_stats$Height[405])^2)*10000
nba_players_stats$Age[405] = 32
nba_players_stats$Team[405] = "MIN"
nba_players_stats$College[405] = "Gonzaga University"
nba_players_stats$Birth_Place[405] = "fr"
nba_players_stats$Birthdate[405] = "13-Jan-83"
#Russell Westbrook
nba_players_stats$Height[410] = 190.5
nba_players_stats$Weight[410] = 200/2.205
nba_players_stats$BMI[410] = (nba_players_stats$Weight[410]/(nba_players_stats$Height[410])^2)*10000
nba_players_stats$Age[410] = 26
nba_players_stats$Team[410] = "OKC"
nba_players_stats$College[410] = "University of California, Los Angeles"
nba_players_stats$Birth_Place[410] = "us"
nba_players_stats$Birthdate[410] = "12-Nov-88"
#Sebastian Telfair
nba_players_stats$Height[416] = 182.88
nba_players_stats$Weight[416] = 170/2.205
nba_players_stats$BMI[416] = (nba_players_stats$Weight[416]/(nba_players_stats$Height[416])^2)*10000
nba_players_stats$Age[416] = 29
nba_players_stats$Team[416] = "OKC"
nba_players_stats$College[416] = "no college"
nba_players_stats$Birth_Place[416] = "us"
nba_players_stats$Birthdate[416] = "9-Jun-85"
#Shabazz Napier
nba_players_stats$Height[421] = 185.42
nba_players_stats$Weight[421] = 181/2.205
nba_players_stats$BMI[421] = (nba_players_stats$Weight[421]/(nba_players_stats$Height[421])^2)*10000
nba_players_stats$Age[421] = 23
nba_players_stats$Team[421] = "MIA"
nba_players_stats$College[421] = "University of Connecticut"
nba_players_stats$Birth_Place[421] = "us"
nba_players_stats$Birthdate[421] = "14-Jul-91"
#Shayne Whittington
nba_players_stats$Height[428] = 208.28
nba_players_stats$Weight[428] = 245/2.205
nba_players_stats$BMI[428] = (nba_players_stats$Weight[428]/(nba_players_stats$Height[428])^2)*10000
nba_players_stats$Age[428] = 23
nba_players_stats$Team[428] = "IND"
nba_players_stats$College[428] = "Western Michigan University"
nba_players_stats$Birth_Place[428] = "us"
nba_players_stats$Birthdate[428] = "27-Mar-91"
#Thaddeus Young
nba_players_stats$Height[444] = 203.2
nba_players_stats$Weight[444] = 220/2.205
nba_players_stats$BMI[444] = (nba_players_stats$Weight[444]/(nba_players_stats$Height[444])^2)*10000
nba_players_stats$Age[444] = 26
nba_players_stats$Team[444] = "MIN"
nba_players_stats$College[444] = "Georgia Institute of Technology"
nba_players_stats$Birth_Place[444] = "us"
nba_players_stats$Birthdate[444] = "21-Jun-88"
#Thomas Robinson
nba_players_stats$Height[445] = 205.74
nba_players_stats$Weight[445] = 238/2.205
nba_players_stats$BMI[445] = (nba_players_stats$Weight[445]/(nba_players_stats$Height[445])^2)*10000
nba_players_stats$Age[445] = 23
nba_players_stats$Team[445] = "POR"
nba_players_stats$College[445] = "University of Kansas"
nba_players_stats$Birth_Place[445] = "us"
nba_players_stats$Birthdate[445] = "17-Mar-91"
#TJ Warren
nba_players_stats$Height[451] = 203.2
nba_players_stats$Weight[451] = 220/2.205
nba_players_stats$BMI[451] = (nba_players_stats$Weight[451]/(nba_players_stats$Height[451])^2)*10000
nba_players_stats$Age[451] = 21
nba_players_stats$Team[451] = "PHX"
nba_players_stats$College[451] = "North Carolina State University"
nba_players_stats$Birth_Place[451] = "us"
nba_players_stats$Birthdate[451] = "5-Sep-93"
#Tony Wroten
nba_players_stats$Height[457] = 198.12
nba_players_stats$Weight[457] = 205/2.205
nba_players_stats$BMI[457] = (nba_players_stats$Weight[457]/(nba_players_stats$Height[457])^2)*10000
nba_players_stats$Age[457] = 21
nba_players_stats$Team[457] = "PHI"
nba_players_stats$College[457] = "University of Washington"
nba_players_stats$Birth_Place[457] = "us"
nba_players_stats$Birthdate[457] = "13-Apr-93"
#Travis Wear
nba_players_stats$Height[459] = 205.74
nba_players_stats$Weight[459] = 218/2.205
nba_players_stats$BMI[459] = (nba_players_stats$Weight[459]/(nba_players_stats$Height[459])^2)*10000
nba_players_stats$Age[459] = 24
nba_players_stats$Team[459] = "NYK"
nba_players_stats$College[459] = "University of North Carolina at Chapel Hill"
nba_players_stats$Birth_Place[459] = "us"
nba_players_stats$Birthdate[459] = "21-Sep-90"
#Tristan Thompson
nba_players_stats$Height[463] = 205.74
nba_players_stats$Weight[463] = 254/2.205
nba_players_stats$BMI[463] = (nba_players_stats$Weight[463]/(nba_players_stats$Height[463])^2)*10000
nba_players_stats$Age[463] = 23
nba_players_stats$Team[463] = "CLE"
nba_players_stats$College[463] = "University of Texas at Austin"
nba_players_stats$Birth_Place[463] = "ca"
nba_players_stats$Birthdate[463] = "13-Mar-91"
#Tyler Zeller
nba_players_stats$Height[469] = 213.36
nba_players_stats$Weight[469] = 253/2.205
nba_players_stats$BMI[469] = (nba_players_stats$Weight[469]/(nba_players_stats$Height[469])^2)*10000
nba_players_stats$Age[469] = 25
nba_players_stats$Team[469] = "BOS"
nba_players_stats$College[469] = "University of North Carolina at Chapel Hill"
nba_players_stats$Birth_Place[469] = "us"
nba_players_stats$Birthdate[469] = "17-Jan-90"
#Tyrus Thomas
nba_players_stats$Height[471] = 208.28
nba_players_stats$Weight[471] = 225/2.205
nba_players_stats$BMI[471] = (nba_players_stats$Weight[471]/(nba_players_stats$Height[471])^2)*10000
nba_players_stats$Age[471] = 28
nba_players_stats$Team[471] = "MEM"
nba_players_stats$College[471] = "Louisiana State University"
nba_players_stats$Birth_Place[471] = "us"
nba_players_stats$Birthdate[471] = "17-Aug-86"
#Al Jefferson
nba_players_stats$College[6] = "no college"
#Alexey Shved
nba_players_stats$College[11] = "no college"
#Alexis Ajinca
nba_players_stats$College[12] = "no college"
#Amir Johnson
nba_players_stats$College[17] = "no college"
#Andrea Bargnani
nba_players_stats$College[24] = "no college"
#Andrei Kirilenko
nba_players_stats$College[25] = "no college"
#Bismack Biyombo
nba_players_stats$College[44] = "no college"
#Bojan Bogdanovic
nba_players_stats$College[46] = "no college"
#Boris Diaw
nba_players_stats$College[47] = "no college"
#Brandon Jennings
nba_players_stats$College[52] = "no college"
#Bruno Caboclo
nba_players_stats$College[58] = "no college"
#CJ Miles
nba_players_stats$College[80] = "no college"
#Clint Capela
nba_players_stats$College[83] = "no college"
#Damjan Rudez
nba_players_stats$College[93] = "no college"
#Danilo Gallinari
nba_players_stats$College[94] = "no college"
#Dante Exum
nba_players_stats$College[98] = "no college"
#Dennis Schroder
nba_players_stats$College[112] = "no college"
#Dirk Nowitzki
nba_players_stats$College[121] = "no college"
#Donatas Motiejunas
nba_players_stats$College[123] = "no college"
#Dorell Wright
nba_players_stats$College[124] = "no college"
#Dwight Howard
nba_players_stats$College[130] = "no college"
#Enes Kanter
nba_players_stats$College[141] = "no college"
#Ersan Ilyasova
nba_players_stats$College[145] = "no college"
#Evan Fournier
nba_players_stats$College[147] = "no college"
#Furkan Aldemir
nba_players_stats$College[151] = "no college"
#Gerald Green
nba_players_stats$College[157] = "no college"
#Giannis Antetokounmpo
nba_players_stats$College[160] = "no college"
#Goran Dragic
nba_players_stats$College[165] = "no college"
#Ian Mahinmi
nba_players_stats$College[180] = "no college"
#Joe Ingles
nba_players_stats$College[234] = "no college"
#Joel Freeland
nba_players_stats$College[237] = "no college"
#Joffrey Lauvergne
nba_players_stats$College[239] = "no college"
#Jonas Jerebko
nba_players_stats$College[247] = "no college"
#Jonas Valanciunas
nba_players_stats$College[248] = "no college"
#Jose Calderon
nba_players_stats$College[255] = "no college"
#JR Smith
nba_players_stats$College[258] = "no college"
#Kendrick Perkins
nba_players_stats$College[269] = "no college"
#Kevin Garnett
nba_players_stats$College[275] = "no college"
#Kevin Seraphin
nba_players_stats$College[278] = "no college"
#Kobe Bryant
nba_players_stats$College[283] = "no college"
#Kostas Papanikolaou
nba_players_stats$College[285] = "no college"
#Leandro Barbosa
nba_players_stats$College[301] = "no college"
#Lebron James
nba_players_stats$College[302] = "no college"
#Lou Williams
nba_players_stats$College[306] = "no college"
#Lucas Nogueira
nba_players_stats$College[308] = "no college"
#Luis Scola
nba_players_stats$College[309] = "no college"
#Manu Ginobili
nba_players_stats$College[314] = "no college"
#Marc Gasol
nba_players_stats$College[315] = "no college"
#Marcin Gortat
nba_players_stats$College[316] = "no college"
#Marco Belinelli
nba_players_stats$College[317] = "no college"
#Monta Ellis
nba_players_stats$College[346] = "no college"
#Nene
nba_players_stats$College[350] = "no college"
#Nicolas Batum
nba_players_stats$College[356] = "no college"
#Nikola Mirotic
nba_players_stats$College[358] = "no college"
#Ognjen Kuzmic
nba_players_stats$College[364] = "no college"
#Omer Asik
nba_players_stats$College[365] = "no college"
#Omri Casspi
nba_players_stats$College[366] = "no college"
#Pablo Prigioni
nba_players_stats$College[368] = "no college"
#Pau Gasol
nba_players_stats$College[373] = "no college"
#Pero Antic
nba_players_stats$College[377] = "no college"
#Ricky Rubio
nba_players_stats$College[397] = "no college"
#Rudy Gobert
nba_players_stats$College[408] = "no college"
#Serge Ibaka
nba_players_stats$College[417] = "no college"
#Sergey Karasev
nba_players_stats$College[418] = "no college"
#Shaun Livingston
nba_players_stats$College[424] = "no college"
#Thabo Sefolosha
nba_players_stats$College[443] = "no college"
#Tiago Splitter
nba_players_stats$College[446] = "no college"
#Timofey Mozgov
nba_players_stats$College[450] = "no college"
#Tony Parker
nba_players_stats$College[455] = "no college"
#Tyson Chandler
nba_players_stats$College[472] = "no college"
#Victor Claver
nba_players_stats$College[475] = "no college"
#Zaza Pachulia
nba_players_stats$College[489] = "no college"
#Zoran Dragic
nba_players_stats$College[490] = "no college"
```
```{r Adding missing position data,echo=FALSE}
nba_players_stats$Pos[16] = "PF"
nba_players_stats$Pos[18] = "C"
nba_players_stats$Pos[28] = "SF"
nba_players_stats$Pos[32] = "PF"
nba_players_stats$Pos[42] = "PG"
nba_players_stats$Pos[49] = "PF"
nba_players_stats$Pos[69] = "PF"
nba_players_stats$Pos[81] = "SG"
nba_players_stats$Pos[84] = "PF"
nba_players_stats$Pos[105] = "PF"
nba_players_stats$Pos[113] = "PG"
nba_players_stats$Pos[116] = "PF"
nba_players_stats$Pos[120] = "SG"
nba_players_stats$Pos[124] = "SF"
nba_players_stats$Pos[132] = "PG"
nba_players_stats$Pos[136] = "C"
nba_players_stats$Pos[138] = "SF"
nba_players_stats$Pos[139] = "PG"
nba_players_stats$Pos[149] = "C"
nba_players_stats$Pos[159] = "PF"
nba_players_stats$Pos[161] = "SF"
nba_players_stats$Pos[164] = "SF"
nba_players_stats$Pos[174] = "C"
nba_players_stats$Pos[175] = "PF"
nba_players_stats$Pos[176] = "C"
nba_players_stats$Pos[177] = "SF"
nba_players_stats$Pos[178] = "SF"
nba_players_stats$Pos[184] = "PG"
nba_players_stats$Pos[187] = "PF"
nba_players_stats$Pos[190] = "SF"
nba_players_stats$Pos[199] = "SG"
nba_players_stats$Pos[205] = "C"
nba_players_stats$Pos[209] = "PF"
nba_players_stats$Pos[210] = "PG"
nba_players_stats$Pos[211] = "C"
nba_players_stats$Pos[217] = "C"
nba_players_stats$Pos[243] = "SF"
nba_players_stats$Pos[244] = "PG"
nba_players_stats$Pos[257] = "PF"
nba_players_stats$Pos[263] = "C"
nba_players_stats$Pos[295] = "PF"
nba_players_stats$Pos[299] = "PF"
nba_players_stats$Pos[320] = "PG"
nba_players_stats$Pos[325] = "SF"
nba_players_stats$Pos[342] = "C"
nba_players_stats$Pos[343] = "PF"
nba_players_stats$Pos[347] = "PG"
nba_players_stats$Pos[348] = "PG"
nba_players_stats$Pos[355] = "SF"
nba_players_stats$Pos[359] = "C"
nba_players_stats$Pos[371] = "PF"
nba_players_stats$Pos[381] = "C"
nba_players_stats$Pos[394] = "SF"
nba_players_stats$Pos[396] = "SG"
nba_players_stats$Pos[400] = "C"
nba_players_stats$Pos[405] = "PF"
nba_players_stats$Pos[410] = "PG"
nba_players_stats$Pos[416] = "PG"
nba_players_stats$Pos[421] = "PG"
nba_players_stats$Pos[428] = "PF"
nba_players_stats$Pos[444] = "PF"
nba_players_stats$Pos[445] = "C"
nba_players_stats$Pos[451] = "PF"
nba_players_stats$Pos[457] = "PG"
nba_players_stats$Pos[459] = "SF"
nba_players_stats$Pos[463] = "PF"
nba_players_stats$Pos[469] = "PF"
nba_players_stats$Pos[471] = "PF"
```
```{r Adding Salary column,echo=FALSE}
nba_players_stats$Salary = NA
nba_players_stats$Salary[1] = 530802
nba_players_stats$Salary[2] = 983595
nba_players_stats$Salary[3] = 4290174
nba_players_stats$Salary[4] = 1993879
nba_players_stats$Salary[5] = 12896187
nba_players_stats$Salary[6] = 14508210
nba_players_stats$Salary[7] = 1371360
nba_players_stats$Salary[8] = 3440454
nba_players_stats$Salary[9] = 230918
nba_players_stats$Salary[10] = 3922504
nba_players_stats$Salary[11] = 3437610
nba_players_stats$Salary[12] = 1054353
nba_players_stats$Salary[13] = 1054353
nba_players_stats$Salary[14] = 926376
nba_players_stats$Salary[15] = 1142799
nba_players_stats$Salary[16] = 23531949
nba_players_stats$Salary[17] = 7522775
nba_players_stats$Salary[18] = 10531886
nba_players_stats$Salary[19] = 291987
nba_players_stats$Salary[20] = 2760170
nba_players_stats$Salary[21] = 13207355
nba_players_stats$Salary[22] = 4970405
nba_players_stats$Salary[23] = 1247577
nba_players_stats$Salary[24] = 12896187
nba_players_stats$Salary[25] = 3574645
nba_players_stats$Salary[26] = 13941824
nba_players_stats$Salary[27] = 1661286
nba_players_stats$Salary[28] = 5922187
nba_players_stats$Salary[29] = 5979446
nba_players_stats$Salary[30] = 6026001
nba_players_stats$Salary[31] = 3438983
nba_players_stats$Salary[32] = 3224046
nba_players_stats$Salary[33] = 1195347
nba_players_stats$Salary[34] = 51614
nba_players_stats$Salary[35] = 2256832
nba_players_stats$Salary[36] = 8127284
nba_players_stats$Salary[37] = 1357913
nba_players_stats$Salary[38] = 2622052
nba_players_stats$Salary[39] = 7728052
nba_players_stats$Salary[40] = 4836070
nba_players_stats$Salary[41] = 3252289
nba_players_stats$Salary[42] = 2232115
nba_players_stats$Salary[43] = 1353857
nba_players_stats$Salary[44] = 4391638
nba_players_stats$Salary[45] = 18949537
nba_players_stats$Salary[46] = 3522808
nba_players_stats$Salary[47] = 8597458
nba_players_stats$Salary[48] = 4841744
nba_players_stats$Salary[49] = 5373411
nba_players_stats$Salary[50] = 7469041
nba_players_stats$Salary[51] = 139360
nba_players_stats$Salary[52] = 8597458
nba_players_stats$Salary[53] = 3819331
nba_players_stats$Salary[54] = 1231247
nba_players_stats$Salary[55] = 10529736
nba_players_stats$Salary[56] = 2936032
nba_players_stats$Salary[57] = 16892930
nba_players_stats$Salary[58] = 1567273
nba_players_stats$Salary[59] = 163566
nba_players_stats$Salary[60] = 2232115
nba_players_stats$Salary[61] = 545225
nba_players_stats$Salary[62] = 7254105
nba_players_stats$Salary[63] = 18054661
nba_players_stats$Salary[64] = 24135645
nba_players_stats$Salary[65] = 4836070
nba_players_stats$Salary[66] = 1231247
nba_players_stats$Salary[67] = 15797829
nba_players_stats$Salary[68] = 9219793
nba_players_stats$Salary[69] = 1415151
nba_players_stats$Salary[70] = 5373411
nba_players_stats$Salary[71] = 5695816
nba_players_stats$Salary[72] = 22186170
nba_players_stats$Salary[73] = 3363755
nba_players_stats$Salary[74] = 983595
nba_players_stats$Salary[75] = 8000000
nba_players_stats$Salary[76] = 5158474
nba_players_stats$Salary[77] = 21567329
nba_players_stats$Salary[78] = 6403763
nba_players_stats$Salary[79] = 2601805
nba_players_stats$Salary[80] = 4519039
nba_players_stats$Salary[81] = 1192639
nba_players_stats$Salary[82] = 545225
nba_players_stats$Salary[83] = 1278012
nba_players_stats$Salary[84] = 4331571
nba_players_stats$Salary[85] = 1054353
nba_players_stats$Salary[86] = 5053693
nba_players_stats$Salary[87] = 545225
nba_players_stats$Salary[88] = 2294009
nba_players_stats$Salary[89] = 5857018
nba_players_stats$Salary[90] = 3224046
nba_players_stats$Salary[91] = 775027
nba_players_stats$Salary[92] = 3590427
nba_players_stats$Salary[93] = 1182150
nba_players_stats$Salary[94] = 11665515
nba_players_stats$Salary[95] = 2256832
nba_players_stats$Salary[96] = 4325596
nba_players_stats$Salary[97] = 894072
nba_players_stats$Salary[98] = 3884976
nba_players_stats$Salary[99] = 983595
nba_players_stats$Salary[100] = 863130
nba_players_stats$Salary[101] = 3715336
nba_players_stats$Salary[102] = 5155964
nba_players_stats$Salary[103] = 16133130
nba_players_stats$Salary[104] = 64143
nba_players_stats$Salary[105] = 32071
nba_players_stats$Salary[106] = 12896187
nba_players_stats$Salary[107] = 12294497
nba_players_stats$Salary[108] = 2149364
nba_players_stats$Salary[109] = 10209481
nba_players_stats$Salary[110] = 14724490
nba_players_stats$Salary[111] = 2686705
nba_players_stats$Salary[112] = 1816943
nba_players_stats$Salary[113] = 21229773
nba_players_stats$Salary[114] = 13917135
nba_players_stats$Salary[115] = 20271598
nba_players_stats$Salary[116] = 7178733
nba_players_stats$Salary[117] = 4168580
nba_players_stats$Salary[118] = 950963
nba_players_stats$Salary[119] = 877458
nba_players_stats$Salary[120] = 4365359
nba_players_stats$Salary[121] = 8570034
nba_players_stats$Salary[122] = 1018973
nba_players_stats$Salary[123] = 1594742
nba_players_stats$Salary[124] = 3379875
nba_players_stats$Salary[125] = 2448083
nba_players_stats$Salary[126] = 983595
nba_players_stats$Salary[127] = 8735543
nba_players_stats$Salary[128] = 79157
nba_players_stats$Salary[129] = 51614
nba_players_stats$Salary[130] = 23037180
nba_players_stats$Salary[131] = 545225
nba_players_stats$Salary[132] = 16120234
nba_players_stats$Salary[133] = 419193
nba_players_stats$Salary[134] = 134447
nba_players_stats$Salary[135] = 1054353
nba_players_stats$Salary[136] = 1054353
nba_players_stats$Salary[137] = 2576916
nba_players_stats$Salary[138] = 323927
nba_players_stats$Salary[139] = 173572
nba_players_stats$Salary[140] = 2149364
nba_players_stats$Salary[141] = 6456805
nba_players_stats$Salary[142] = 13970869
nba_players_stats$Salary[143] = 16011624
nba_players_stats$Salary[144] = 545225
nba_players_stats$Salary[145] = 8489990
nba_players_stats$Salary[146] = 1018973
nba_players_stats$Salary[147] = 1594742
nba_players_stats$Salary[148] = 3522808
nba_players_stats$Salary[149] = 1195992
nba_players_stats$Salary[150] = 1415151
nba_players_stats$Salary[151] = 3020185
nba_players_stats$Salary[152] = 954880
nba_players_stats$Salary[153] = 1054353
nba_players_stats$Salary[154] = 1632657
nba_players_stats$Salary[155] = 3492717
nba_players_stats$Salary[156] = 8597458
nba_players_stats$Salary[157] = 3761387
nba_players_stats$Salary[158] = 6448093
nba_players_stats$Salary[159] = 10860583
nba_players_stats$Salary[160] = 2013094
nba_players_stats$Salary[161] = 1880693
nba_players_stats$Salary[162] = 8412596
nba_players_stats$Salary[163] = 505828
nba_players_stats$Salary[164] = 545224
nba_players_stats$Salary[165] = 8060117
nba_players_stats$Salary[166] = 15847264
nba_players_stats$Salary[167] = 1519041
nba_players_stats$Salary[168] = 877458
nba_players_stats$Salary[169] = 5889186
nba_players_stats$Salary[170] = 1018973
nba_players_stats$Salary[171] = 1054353
nba_players_stats$Salary[172] = 6877966
nba_players_stats$Salary[173] = 3277694
nba_players_stats$Salary[174] = 833083
nba_players_stats$Salary[175] = 1448490
nba_players_stats$Salary[176] = 983595
nba_players_stats$Salary[177] = 334907
nba_players_stats$Salary[178] = 877458
nba_players_stats$Salary[179] = 877456
nba_players_stats$Salary[180] = 4298729
nba_players_stats$Salary[181] = 2967319
nba_players_stats$Salary[182] = 877458
nba_players_stats$Salary[183] = 7779201
nba_players_stats$Salary[184] = 305867
nba_players_stats$Salary[185] = 6256883
nba_players_stats$Salary[186] = 112250
nba_players_stats$Salary[187] = 5298785
nba_players_stats$Salary[188] = 163565
nba_players_stats$Salary[189] = 983595
nba_players_stats$Salary[190] = 545225
nba_players_stats$Salary[191] = 929072
nba_players_stats$Salary[192] = 5857018
nba_players_stats$Salary[193] = 5104740
nba_players_stats$Salary[194] = 545225
nba_players_stats$Salary[195] = 15791280
nba_players_stats$Salary[196] = 2686705
nba_players_stats$Salary[197] = 1556666
nba_players_stats$Salary[198] = 279024
nba_players_stats$Salary[199] = 1799533
nba_players_stats$Salary[200] = 262986
nba_players_stats$Salary[201] = 1556666
nba_players_stats$Salary[202] = 398400
nba_players_stats$Salary[203] = 4567399
nba_players_stats$Salary[204] = 1530906
nba_players_stats$Salary[205] = 545225
nba_players_stats$Salary[206] = 6770498
nba_players_stats$Salary[207] = 1415151
nba_players_stats$Salary[208] = 7094112
nba_players_stats$Salary[209] = 3522808
nba_players_stats$Salary[210] = 5857018
nba_players_stats$Salary[211] = 6488394
nba_players_stats$Salary[212] = 12090175
nba_players_stats$Salary[213] = 1308637
nba_players_stats$Salary[214] = 1965325
nba_players_stats$Salary[215] = 9887077
nba_players_stats$Salary[216] = 8597458
nba_players_stats$Salary[217] = 877458
nba_players_stats$Salary[218] = 983595
nba_players_stats$Salary[219] = 950963
nba_players_stats$Salary[220] = 64143
nba_players_stats$Salary[221] = 1929054
nba_players_stats$Salary[222] = 2366450
nba_players_stats$Salary[223] = 16011624
nba_players_stats$Salary[224] = 877458
nba_players_stats$Salary[225] = 507336
nba_players_stats$Salary[226] = 3224046
nba_players_stats$Salary[227] = 1018973
nba_players_stats$Salary[228] = 2277481
nba_players_stats$Salary[229] = 5783671
nba_players_stats$Salary[230] = 7299779
nba_players_stats$Salary[231] = 13648465
nba_players_stats$Salary[232] = 6448093
nba_players_stats$Salary[233] = 950963
nba_players_stats$Salary[234] = 545225
nba_players_stats$Salary[235] = 24911984
nba_players_stats$Salary[236] = 4083792
nba_players_stats$Salary[237] = 3331515
nba_players_stats$Salary[238] = 1018973
nba_players_stats$Salary[239] = 1923983
nba_players_stats$Salary[240] = 2135737
nba_players_stats$Salary[241] = 1410971
nba_players_stats$Salary[242] = 528709
nba_players_stats$Salary[243] = 1074682
nba_players_stats$Salary[244] = 14724490
nba_players_stats$Salary[245] = 644809
nba_players_stats$Salary[246] = 1039755
nba_players_stats$Salary[247] = 4836070
nba_players_stats$Salary[248] = 3953068
nba_players_stats$Salary[249] = 1444501
nba_players_stats$Salary[250] = 545225
nba_players_stats$Salary[251] = 2256832
nba_players_stats$Salary[252] = 1324663
nba_players_stats$Salary[253] = 9672140
nba_players_stats$Salary[254] = 1032302
nba_players_stats$Salary[255] = 7627225
nba_players_stats$Salary[256] = 5701189
nba_players_stats$Salary[257] = 16061961
nba_players_stats$Salary[258] = 6429152
nba_players_stats$Salary[259] = 11821505
nba_players_stats$Salary[260] = 3221209
nba_players_stats$Salary[261] = 877458
nba_players_stats$Salary[262] = 877458
nba_players_stats$Salary[263] = 1894320
nba_players_stats$Salary[264] = 185928
nba_players_stats$Salary[265] = 3281400
nba_players_stats$Salary[266] = 2230782
nba_players_stats$Salary[267] = 3709999
nba_players_stats$Salary[268] = 983595
nba_players_stats$Salary[269] = 10305008
nba_players_stats$Salary[270] = 2550798
nba_players_stats$Salary[271] = 2149364
nba_players_stats$Salary[272] = 2979535
nba_players_stats$Salary[273] = 879142
nba_players_stats$Salary[274] = 21490972
nba_players_stats$Salary[275] = 12896187
nba_players_stats$Salary[276] = 16892998
nba_players_stats$Salary[277] = 7299779
nba_players_stats$Salary[278] = 4189854
nba_players_stats$Salary[279] = 983595
nba_players_stats$Salary[280] = 2933882
nba_players_stats$Salary[281] = 545225
nba_players_stats$Salary[282] = 3305593
nba_players_stats$Salary[283] = 25255033
nba_players_stats$Salary[284] = 3224046
nba_players_stats$Salary[285] = 5155964
nba_players_stats$Salary[286] = 4567399
nba_players_stats$Salary[287] = 1175358
nba_players_stats$Salary[288] = 6720548
nba_players_stats$Salary[289] = 12896187
nba_players_stats$Salary[290] = 983595
nba_players_stats$Salary[291] = 1171403
nba_players_stats$Salary[292] = 8017048
nba_players_stats$Salary[293] = 16335170
nba_players_stats$Salary[294] = 9672140
nba_players_stats$Salary[295] = 1006981
nba_players_stats$Salary[296] = 9134799
nba_players_stats$Salary[297] = 317520
nba_players_stats$Salary[298] = 57727
nba_players_stats$Salary[299] = 11821505
nba_players_stats$Salary[300] = 1018973
nba_players_stats$Salary[301] = 1556666
nba_players_stats$Salary[302] = 22186170
nba_players_stats$Salary[303] = 119878
nba_players_stats$Salary[304] = 419214
nba_players_stats$Salary[305] = 1391571
nba_players_stats$Salary[306] = 5857018
nba_players_stats$Salary[307] = 4709876
nba_players_stats$Salary[308] = 1894320
nba_players_stats$Salary[309] = 4836070
nba_players_stats$Salary[310] = 1054353
nba_players_stats$Salary[311] = 2955376
nba_players_stats$Salary[312] = 10439959
nba_players_stats$Salary[313] = 767226
nba_players_stats$Salary[314] = 7522775
nba_players_stats$Salary[315] = 17011885
nba_players_stats$Salary[316] = 11214075
nba_players_stats$Salary[317] = 3088368
nba_players_stats$Salary[318] = 3337211
nba_players_stats$Salary[319] = 3528525
nba_players_stats$Salary[320] = 9347049
nba_players_stats$Salary[321] = 4298729
nba_players_stats$Salary[322] = 545225
nba_players_stats$Salary[323] = 3389397
nba_players_stats$Salary[324] = 3930650
nba_players_stats$Salary[325] = 5783671
nba_players_stats$Salary[326] = 7522775
nba_players_stats$Salary[327] = 1458429
nba_players_stats$Salary[328] = 3649889
nba_players_stats$Salary[329] = 1556666
nba_players_stats$Salary[330] = 877458
nba_players_stats$Salary[331] = 2028828
nba_players_stats$Salary[332] = 2491027
nba_players_stats$Salary[333] = 354886
nba_players_stats$Salary[334] = 2471812
nba_players_stats$Salary[335] = 5391638
nba_players_stats$Salary[336] = 9414216
nba_players_stats$Salary[337] = 3224046
nba_players_stats$Salary[338] = 10028935
nba_players_stats$Salary[339] = 877458
nba_players_stats$Salary[340] = 3582273
nba_players_stats$Salary[341] = 1257249
nba_players_stats$Salary[342] = 1715252
nba_players_stats$Salary[343] = 3619637
nba_players_stats$Salary[344] = 1504598
nba_players_stats$Salary[345] = 3965074
nba_players_stats$Salary[346] = 9371229
nba_players_stats$Salary[347] = 2264054
nba_players_stats$Salary[348] = 972429
nba_players_stats$Salary[349] = 1556666
nba_players_stats$Salary[350] = 13970869
nba_players_stats$Salary[351] = 3562700
nba_players_stats$Salary[352] = 877458
nba_players_stats$Salary[353] = 2409440
nba_players_stats$Salary[354] = 545225
nba_players_stats$Salary[355] = 5367414
nba_players_stats$Salary[356] = 12241168
nba_players_stats$Salary[357] = 2950905
nba_players_stats$Salary[358] = 5701189
nba_players_stats$Salary[359] = 13003655
nba_players_stats$Salary[360] = 3119541
nba_players_stats$Salary[361] = 2712713
nba_players_stats$Salary[362] = 2310768
nba_players_stats$Salary[363] = 8597458
nba_players_stats$Salary[364] = 877458
nba_players_stats$Salary[365] = 16011624
nba_players_stats$Salary[366] = 1142799
nba_players_stats$Salary[367] = 4804345
nba_players_stats$Salary[368] = 1787154
nba_players_stats$Salary[369] = 983595
nba_players_stats$Salary[370] = 379010
nba_players_stats$Salary[371] = 6266822
nba_players_stats$Salary[372] = 3761387
nba_players_stats$Salary[373] = 7660335
nba_players_stats$Salary[374] = 16979980
nba_players_stats$Salary[375] = 10209481
nba_players_stats$Salary[376] = 5701189
nba_players_stats$Salary[377] = 1343352
nba_players_stats$Salary[378] = 1213531
nba_players_stats$Salary[379] = 877458
nba_players_stats$Salary[380] = 1235583
nba_players_stats$Salary[381] = 6125689
nba_players_stats$Salary[382] = 983595
nba_players_stats$Salary[383] = 428145
nba_players_stats$Salary[384] = 3381023
nba_players_stats$Salary[385] = 13873170
nba_players_stats$Salary[386] = 2232115
nba_players_stats$Salary[387] = 3224046
nba_players_stats$Salary[388] = 1556666
nba_players_stats$Salary[389] = 877458
nba_players_stats$Salary[390] = 4685614
nba_players_stats$Salary[391] = 1290392
nba_players_stats$Salary[392] = 1900741
nba_players_stats$Salary[393] = 2499367
nba_players_stats$Salary[394] = 524342
nba_players_stats$Salary[395] = 1556666
nba_players_stats$Salary[396] = 1032302
nba_players_stats$Salary[397] = 5449376
nba_players_stats$Salary[398] = 945720
nba_players_stats$Salary[399] = 1074682
nba_players_stats$Salary[400] = 983595
nba_players_stats$Salary[401] = 5739049
nba_players_stats$Salary[402] = 1386727
nba_players_stats$Salary[403] = 1319693
nba_players_stats$Salary[404] = 1415151
nba_players_stats$Salary[405] = 1719491
nba_players_stats$Salary[406] = 16011624
nba_players_stats$Salary[407] = 20759988
nba_players_stats$Salary[408] = 1211596
nba_players_stats$Salary[409] = 545225
nba_players_stats$Salary[410] = 16892997
nba_players_stats$Salary[411] = 9125664
nba_players_stats$Salary[412] = 1408141
nba_players_stats$Salary[413] = 1773225
nba_players_stats$Salary[414] = 2026587
nba_players_stats$Salary[415] = 32071
nba_players_stats$Salary[416] = 1415151
nba_players_stats$Salary[417] = 13164857
nba_players_stats$Salary[418] = 1648390
nba_players_stats$Salary[419] = 51614
nba_players_stats$Salary[420] = 2119230
nba_players_stats$Salary[421] = 1331144
nba_players_stats$Salary[422] = 1726025
nba_players_stats$Salary[423] = 231928
nba_players_stats$Salary[424] = 5701189
nba_players_stats$Salary[425] = 1319693
nba_players_stats$Salary[426] = 1556666
nba_players_stats$Salary[427] = 1231246
nba_players_stats$Salary[428] = 545225
nba_players_stats$Salary[429] = 2615059
nba_players_stats$Salary[430] = 37613
nba_players_stats$Salary[431] = 1400139
nba_players_stats$Salary[432] = 752277
nba_players_stats$Salary[433] = 5701189
nba_players_stats$Salary[434] = 11423026
nba_players_stats$Salary[435] = 2256832
nba_players_stats$Salary[436] = 3703298
nba_players_stats$Salary[437] = 2348137
nba_players_stats$Salary[438] = 8597458
nba_players_stats$Salary[439] = 545225
nba_players_stats$Salary[440] = 8283505
nba_players_stats$Salary[441] = 1739566
nba_players_stats$Salary[442] = 3002619
nba_players_stats$Salary[443] = 4298729
nba_players_stats$Salary[444] = 9845024
nba_players_stats$Salary[445] = 3953067
nba_players_stats$Salary[446] = 9940811
nba_players_stats$Salary[447] = 11135262
nba_players_stats$Salary[448] = 115458
nba_players_stats$Salary[449] = 1344040
nba_players_stats$Salary[450] = 4997272
nba_players_stats$Salary[451] = 2098983
nba_players_stats$Salary[452] = 2698991
nba_players_stats$Salary[453] = 289060
nba_players_stats$Salary[454] = 5373411
nba_players_stats$Salary[455] = 13433528
nba_players_stats$Salary[456] = 1582362
nba_players_stats$Salary[457] = 1300451
nba_players_stats$Salary[458] = 1074682
nba_players_stats$Salary[459] = 545225
nba_players_stats$Salary[460] = 9242267
nba_players_stats$Salary[461] = 5373411
nba_players_stats$Salary[462] = 2738892
nba_players_stats$Salary[463] = 5826103
nba_players_stats$Salary[464] = 877458
nba_players_stats$Salary[465] = 12461484
nba_players_stats$Salary[466] = 1709518
nba_players_stats$Salary[467] = 3574645
nba_players_stats$Salary[468] = 301476
nba_players_stats$Salary[469] = 1831000
nba_players_stats$Salary[470] = 12106743
nba_players_stats$Salary[471] = 10167207
nba_players_stats$Salary[472] = 15687016
nba_players_stats$Salary[473] = 2936032
nba_players_stats$Salary[474] = 51614
nba_players_stats$Salary[475] = 1472314
nba_players_stats$Salary[476] = 5349983
nba_players_stats$Salary[477] = 4204136
nba_players_stats$Salary[478] = 1142799
nba_players_stats$Salary[479] = 1054353
nba_players_stats$Salary[480] = 7786760
nba_players_stats$Salary[481] = 983595
nba_players_stats$Salary[482] = 3133674
nba_players_stats$Salary[483] = 114525
nba_players_stats$Salary[484] = 1556666
nba_players_stats$Salary[485] = 7259385
nba_players_stats$Salary[486] = 1162806
nba_players_stats$Salary[487] = 2209374
nba_players_stats$Salary[488] = 17732257
nba_players_stats$Salary[489] = 5588347
nba_players_stats$Salary[490] = 1887679
```
```{r Adding missing data to experience column,echo=FALSE}
levels(nba_players_stats$Experience) <- c(levels(nba_players_stats$Experience), 0)
nba_players_stats$Experience[nba_players_stats$Experience == "R"] = "0"
nba_players_stats$Experience[16] = 11
nba_players_stats$Experience[18] = 10
nba_players_stats$Experience[28] = 0
nba_players_stats$Experience[32] = 6
nba_players_stats$Experience[42] = 10
nba_players_stats$Experience[49] = 7
nba_players_stats$Experience[69] = 9
nba_players_stats$Experience[81] = 0
nba_players_stats$Experience[84] = 1
nba_players_stats$Experience[105] = 0
nba_players_stats$Experience[113] = 9
nba_players_stats$Experience[116] = 3
nba_players_stats$Experience[120] = 2
nba_players_stats$Experience[124] = 10
nba_players_stats$Experience[132] = 12
nba_players_stats$Experience[136] = 4
nba_players_stats$Experience[138] = 0
nba_players_stats$Experience[139] = 2 
nba_players_stats$Experience[149] = 1
nba_players_stats$Experience[159] = 15
nba_players_stats$Experience[161] = 1
nba_players_stats$Experience[164] = 0
nba_players_stats$Experience[174] = 2
nba_players_stats$Experience[175] = 15
nba_players_stats$Experience[176] = 2
nba_players_stats$Experience[177] = 5
nba_players_stats$Experience[178] = 1
nba_players_stats$Experience[184] = 4
nba_players_stats$Experience[187] = 0
nba_players_stats$Experience[190] = 0
nba_players_stats$Experience[199] = 0
nba_players_stats$Experience[205] = 0
nba_players_stats$Experience[209] = 6
nba_players_stats$Experience[210] = 15
nba_players_stats$Experience[211] = 6
nba_players_stats$Experience[217] = 1
nba_players_stats$Experience[243] = 12
nba_players_stats$Experience[244] = 4
nba_players_stats$Experience[257] = 10
nba_players_stats$Experience[263] = 0
nba_players_stats$Experience[295] = 3
nba_players_stats$Experience[299] = 4
nba_players_stats$Experience[320] = 5
nba_players_stats$Experience[325] = 9
nba_players_stats$Experience[342] = 1
nba_players_stats$Experience[343] = 2
nba_players_stats$Experience[347] = 9
nba_players_stats$Experience[348] = 1
nba_players_stats$Experience[355] = 7
nba_players_stats$Experience[359] = 4
nba_players_stats$Experience[371] = 4
nba_players_stats$Experience[381] = 3
nba_players_stats$Experience[394] = 5
nba_players_stats$Experience[396] = 1
nba_players_stats$Experience[400] = 2
nba_players_stats$Experience[405] = 9
nba_players_stats$Experience[410] = 6
nba_players_stats$Experience[416] = 9 
nba_players_stats$Experience[421] = 0
nba_players_stats$Experience[428] = 0
nba_players_stats$Experience[444] = 7
nba_players_stats$Experience[445] = 2
nba_players_stats$Experience[451] = 0
nba_players_stats$Experience[457] = 2
nba_players_stats$Experience[459] = 0
nba_players_stats$Experience[463] = 3
nba_players_stats$Experience[469] = 2
nba_players_stats$Experience[471] = 7
nba_players_stats$Experience <- as.numeric(as.character(nba_players_stats$Experience))
```
```{r Adding Team Name,echo=FALSE}
nba_players_stats$Team[7] = "BKN"
nba_players_stats$Team[46] = "BKN"
nba_players_stats$Team[25] = "BKN"
nba_players_stats$Team[57] = "BKN"
nba_players_stats$Team[87] = "BKN"
nba_players_stats$Team[100] = "BKN"
nba_players_stats$Team[134] = "BKN"
nba_players_stats$Team[206] = "BKN"
nba_players_stats$Team[224] = "BKN"
nba_players_stats$Team[235] = "BKN"
nba_players_stats$Team[322] = "BKN"
nba_players_stats$Team[327] = "BKN"
nba_players_stats$Team[418] = "BKN"
nba_players_stats$Team[1] = "PHX"
nba_players_stats$Team[10] = "PHX"
nba_players_stats$Team[33] = "PHX"
nba_players_stats$Team[53] = "PHX"
nba_players_stats$Team[133] = "PHX"
nba_players_stats$Team[142] = "PHX"
nba_players_stats$Team[157] = "PHX"
nba_players_stats$Team[165] = "PHX"
nba_players_stats$Team[220] = "PHX"
nba_players_stats$Team[318] = "PHX"
nba_players_stats$Team[323] = "PHX"
nba_players_stats$Team[341] = "PHX"
nba_players_stats$Team[391] = "PHX"
nba_players_stats$Team[419] = "PHX"
nba_players_stats$Team[466] = "PHX"
nba_players_stats$Team[490] = "PHX"
nba_players_stats$Team[12] = "NOP"
nba_players_stats$Team[30] = "NOP"
nba_players_stats$Team[38] = "NOP"
nba_players_stats$Team[97] = "NOP"
nba_players_stats$Team[99] = "NOP"
nba_players_stats$Team[143] = "NOP"
nba_players_stats$Team[152] = "NOP"
nba_players_stats$Team[227] = "NOP"
nba_players_stats$Team[259] = "NOP"
nba_players_stats$Team[310] = "NOP"
nba_players_stats$Team[362] = "NOP"
nba_players_stats$Team[365] = "NOP"
nba_players_stats$Team[384] = "NOP"
nba_players_stats$Team[411] = "NOP"
nba_players_stats$Team[453] = "NOP"
nba_players_stats$Team[470] = "NOP"

```
```{r Adding column which indicates if team made the Playoffs,echo=FALSE}
nba_players_stats$Playoffs.made = NA
nba_players_stats$Playoffs.made <- ifelse(nba_players_stats$Team == "GSW" | nba_players_stats$Team == "ATL" | nba_players_stats$Team == "BKN" | nba_players_stats$Team == "CLE" | nba_players_stats$Team == "BOS" | nba_players_stats$Team == "LAC" | nba_players_stats$Team == "MIL" | nba_players_stats$Team == "TOR", 'Yes', 'No')
```

$$\textbf{\underline{Analyzing the Data:}}$$
After cleaning the dataset and making sure that there were no NA's, I decided to explore the dataset. Instead of using the traditional graphs in the Base R package, I decided to use Tidyverse and incorporate ggplot2 to create more aesthetically pleasing graphs.
```{r Loading libraries tidyverse and GGplot,echo = T,echo=FALSE,include=FALSE}
library(tidyverse)
library(ggplot2)
```
```{r Plot 1,out.width="50%",fig.align="center",echo=FALSE,fig.cap="Plot 1"}
nba_players_stats %>%
  ggplot()+
  geom_boxplot(aes(Pos,PTS,fill = Playoffs.made))+
  ggtitle("Position in the NBA compared to points made")+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(x = "Position in the NBA",y = "Points made overall",caption = "Data Source: 2014-2015 NBA Players",fill = "Player made Playoffs:")
```
Based on this box-and-whisker plot, this shows that a majority of the players that made the most points overall in the 2014-2015 season were Point Guards regardless if they made the playoffs or not. This makes sense because a Point Guards role in the offense is to run the offense by controlling the ball and is also considered the leader of the team. Thus, it makes sense that the Point Guard on average would shoot more often and thus make more shots on average compared to other positions in the NBA.
```{r finding max BMI,echo=FALSE,echo=FALSE}
x = max(nba_players_stats$BMI)
```
A full season in the NBA is 82 games. Noticeably in plot 2, it shows that the majority of the players that played in the 2014-2015 season that played a majority of the games, there BMI, was respectively in between 24-28 which indicates a healthy relation in weight and height. The outlier however, the player with the BMI of \textcolor{red}{`r round(x,2)`} upon looking at the plot, only seemed to play around 10 games. Using tidyverse, I found that it was Simon Bhullar, who only played 3 games and had a relatively poor performance, and has averaged only 3 minutes and made only 2 points. There could be a possibility that he didn't end up playing after because of an injury or maybe he simply wasn't good enough. Upon searching up his name on the internet, I found an article saying that he had been released by his team, the Sacramento Kings,that year with only a short stint with the team because he just was not up to par in the NBA. I also noticed that they could have signed him as a marketing technique concluding that he was the first of an Indian descent to play in the NBA. It also turns out that he had weight problems and was just seen as too big and not fit for the NBA \textcolor{blue}{\cite{bhullar}}.It seems like the NBA does care about weight and other aspects as well because after that no team in the NBA took him despite only playing 3 games and not yet proving himself. Despite his young age,no team was willing to take a chance on him, which shows to think that teams in the NBA do care about the weight and try to calculate how much the impact can have on the court. I than wanted to see how many people were motivated by the money and thus let their body gain in weight and thus raise their BMI. I put a salary greater than 5 million in the NBA because I personally believe anything greater than 5 million in the NBA is a lot. I also filtered through their BMI saying that if their BMI is greater than 25, they will be shown in the chart because according to BMI, anything greater than 25 is considered  “overweight”.
```{r Plot 2, echo=FALSE, fig.align="center", fig.cap="Plot 2", warning=FALSE, out.width="50%"}
nba_players_stats %>%
  ggplot()+
  geom_point(aes(Games.Played,BMI,color = Pos)) +
  geom_smooth(aes(Games.Played,BMI),color = "red",method = "loess")+
  ggtitle("Games Played in relation to the Players' BMI")+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(x = "Number of Games Played",caption = "Data Source: 2014-2015 NBA Players",color = "Position:")
```

```{r Finding who the highest BMI dude in NBA,include=FALSE}
nba_players_stats %>%
  filter(BMI > 32) %>%
  select(Name,Age,MIN,PTS,Weight,Height,BMI)
```

\begin{figure}[ht]
  \centering\includegraphics[angle = 0,scale = .5]{bhullarr}
  \caption{Simon Bhullar pictured above}
\end{figure}


```{r finding specialized filters,include=FALSE}
nba_players_stats %>%
  filter(BMI > 25 & Salary > 5000000) %>%
  select(Name,Salary) %>%
  n_distinct()

nba_players_stats %>%
  filter(Salary > 5000000) %>%
  select(Name,Salary) %>%
  n_distinct()
```
Surprisingly, it was 103/157 people whose BMI was greater than 25 and salary greater than 5,000,000 compared to the salary greater than 5,000,000 thus meaning that \textcolor{red}{65.6\%} of NBA players in this range have a BMI that is considered "overweight". I then checked their performance on the court to see if money maybe had a factor along with BMI.
```{r finding specialized filters again,include=FALSE}
nba_players_stats %>%
  filter(BMI > 25 & Salary > 5000000 & PTS <  1000 & Games.Played < 60) %>%
  select(Name,Games.Played,PTS) %>%
  n_distinct()
```
```{r finding average points,include=FALSE}
mean_points = nba_players_stats %>%
  filter(BMI > 25 & Salary > 5000000 & PTS <  1000 & Games.Played < 60) %>%
  summarise(mean_points = mean(PTS)/82,mean_salary = mean(Salary))
```
It seems like \textcolor{red}{15.9\%} (25/157) NBA players' commanded huge salaries and yet only scored less than a 1000 points overall in the season thus averaging approximately only \textcolor{red}{`r round(mean_points[1],2)`} points per game. I also calculated the average salary per nba player in this filter, and it thus shows that the average salary for NBA players in this case is \textcolor{red}{`r mean_points[2]`} per player. That is extremely high and shows that either a majority of these players are injured, or are commanding a huge salary and are not trying as hard to earn that salary because they are averaging very few points per game with their BMI being considered in the "overweight" & "obese" category. Although it seems like approximately \textcolor{red}{16\%} of NBA players are not trying hard enough it begs to differ that maybe if they tried harder in expectations of what the team had when they offered that salary, they quite possibly have led their team to the playoffs.
```{r finding players who made the playoffs with high BMi and high pay,include=FALSE}
nba_players_stats %>%
  filter(BMI > 25 & Salary > 5000000 & PTS <  1000 & Games.Played < 60 & Playoffs.made == "Yes") %>%
  select(Name) %>%
  n_distinct()
```
Upon analyzing the playoffs column, I realized that out of the players that commanded huge salaries and had a BMI over the "fit" category, noticeably only \textcolor{red}{24\%} (6/25) players made it to the playoffs. However, despite the fact that I did notice that BMI does have an effect, I noticed that out of all the teams that made it to the playoffs, the Cleveland Cavaliers who had the heaviest team in terms of BMI in the playoffs made it to the Finals. I than realize that just analyzing the data is not enough because it can be misleading and will thus turn to machine learning techniques to figure out if there are factors that affect a performance of an NBA player.
```{r Plot 3,out.width="50%",fig.align="center",echo=FALSE,fig.cap="Plot 3"}
nba_players_stats %>%
  filter(Playoffs.made == "Yes") %>%
  group_by(Team) %>%
  summarise(Average.BMI = mean(BMI)) %>%
  ggplot() +
  geom_point(aes(Team,Average.BMI),color = "magenta")+
  ggtitle("Playoff Teams in relation to average BMI") +
  theme(plot.title = element_text(hjust = 0.5))+
  labs(caption = "Data Source: 2014-2015 NBA Players",y = "Average BMI")
```

$$\textbf{\underline{Machine Learning Analysis:}}$$
I will start by doing an Cross Validation Lasso to see what variables would be nice with the regressor being BMI. We will do this by estimating the vector of parameters $\beta$ from the Lasso model:
$$\hat{\beta} = argmin\sum_{i=1}^n(yi-x^\prime)^2+\lambda\sum_{j=1}^p|\beta_j|$$
I am using Cross-Validation Lasso to pick the true $\lambda$ that can lead to the true prediction error and also picks the best model by penalizing more complicated models. I am also using Cross-Validation Lasso over other best model fits solely because it is one of the best ways to minimize the OOS errors.  
```{r,include=FALSE}
library(gamlr)
model = glm(BMI~.+PTS*MIN+Age*EFF+PF*TOV+BLK*STL,data = nba_players_stats)
x = model.matrix(model)[,-34]
y = nba_players_stats$BMI
fit = cv.gamlr(x,y)
```
```{r,echo=FALSE,fig.align="center", fig.cap="Plot 4", warning=FALSE, out.width="50%"}
plot(fit)
```
```{r,echo=FALSE,fig.align="center", fig.cap="Plot 5", warning=FALSE, out.width="50%"}
spender = gamlr(x,y)
plot(spender)
```

This graph shows that there is not that much variability in terms of BMI and thus there is not much we can do to predict it. This graph is basically I suspect that the best models to predict BMI are the complex ones.

```{r,echo=FALSE,include=FALSE}
lol = predict(fit,newdata = x)
gay = lol[1,]
duh = nba_players_stats$BMI[1]
```
I then predicted the in sample deviance and found that for the person I predicted it on was pretty accurate, with it being pretty close with the real BMI. The real BMI of AJ Price was \textcolor{red}{`r duh`} and the predicted BMI was \textcolor{red}{`r gay`}, which is fairly accurate. I will also be doing now a Nonparametric Bootstrap to essentially see a fairly accurate standard error for the BMI column of my dataset. 
```{r,echo=FALSE,include=FALSE}
B = 100
N = nrow(nba_players_stats)
p_hat =rep(NaN,B)
for(b in 1:B) {
  bssample =sample.int(N, replace=TRUE)
  bsX = x[bssample,]
  bsy = nba_players_stats$BMI[bssample]
  bsmodel =cv.gamlr(bsX, bsy, family = "gaussian")
  bspredict =predict(bsmodel, newdata = x, type = "response")
  p_hat[b] = bspredict
}
```
```{r,echo=FALSE,fig.align="center", fig.cap="Plot 6", warning=FALSE, out.width="50%"}
hist(p_hat)
```
```{r,echo=FALSE}
hehe = (mean(nba_players_stats$BMI)+c(-1,1)*1.96*sd(p_hat,na.rm = TRUE))
```
Based off the bootstrap and thus after making an confidence interval, I found that a majority of the players BMI would be between the confidence interval of `r hehe`.
Based off of this histogram, I see that there is a lot of variability and that it is skewed to the left. This has come to my conclusion that we can predict BMI based off on a multitude of factors. However, I have yet to try an out-of sample prediction for BMI. My next step in this project would be to than try to estimate an out-of sample prediction for BMI based off of a lot of variables. I do believe that it is possible to calculate in sample prediction for BMI based of on the performances of an NBA player on the field including his salary as well.However, to answer my questions about whether performance in the NBA is related to more than the physical attributes of an athlete I believe there is more to it because my predictions, while accurate are still off and thus I do believe that there are more factors that we need to even more accurately predict BMI of an NBA player. 


\begin{thebibliography}{9}
\bibitem{baseball} History Staff: Who Invented Baseball?,\\\texttt{https://www.history.com/news/who-invented-baseball}
\bibitem{viewership} Richard,\\\texttt{https://www.si.com/media/2016/06/20/nba-finals-game-7-tv-ratings-viewers-cavaliers-warriors}
\bibitem{cpi} Inflation Calculator,\\\texttt{https://www.davemanuel.com/inflation-calculator.php}
\bibitem{lebron} LeBron James NBA Salary,\\\texttt{https://hoopshype.com/player/lebron-james/salary/}
\bibitem{mikan} George Mikan Stats,\\\texttt{https://www.basketball-reference.com/players/m/mikange01.html}
\bibitem{lebronppg} Lebron James Stats,\\\texttt{https://www.basketball-reference.com/players/j/jamesle01.html}
\bibitem{shotclock} Keely Flanagan: Basketball's Shot Clock: A Brief History,\\\texttt{https://www.wbur.org/onlyagame/2015/04/22/nba-shot-clock-history-basketball}
\bibitem{dataset} Omri Goldstein: NBA Players Stats - 2014-2015,\\\texttt{https://www.kaggle.com/drgilermo/nba-players-stats-20142015}
\bibitem{Shaq} Associated Press: Athlete Study Exposes Flaw of BMI Obesity Measure,\\\texttt{https://www.foxnews.com/story/athlete-study-exposes-flaw-of-bmi-obesity-measure}
\bibitem{money} Brian Hutchinson: NBA Players Don't Play to Win, They Play for the Money,\\\texttt{https://bleacherreport.com/articles/82851-nba-players-dont-play-to-win-they-play-for-the-money}
\bibitem{fillna} Basketball Stats and History Statistics, scores, and history for the NBA,\\\texttt{https://www.basketball-reference.com}
\bibitem{nba_salary} NBA Players Salaries during the 2014-2015 season,\\\texttt{https://hoopshype.com/salaries/2014-2015/}
\bibitem{bhullar} Ailene Voisin: Opinion: With weight down, Sim Bhullar’s game is on the rise,\\\texttt{https://www.sacbee.com/sports/spt-columns-blogs/ailene-voisin/article16700834.html}
\end{thebibliography}

